Setting up Data

### 2020-06-09 src/SetupData.Rmd
reducing redundancies standardizing DFs

```{r remove.non.foci, echo=FALSE}
#length( Curated_BivData %>% filter(hand.foci.count == "NA") )#36
str(Curated_BivData)
table(Curated_BivData$hand.foci.count, exclude = NULL)
#there are ~600 rows with SC and no hand foci count
table( (Curated_BivData %>% filter(  is.na(hand.foci.count) ) )$category )
#KAZ male and WSB female have >100 observations without hand.foci.counts

#Remove bivalent entries without hand foci count values
cleanCurated_BivData <-  Curated_BivData  %>%  filter(hand.foci.count  == 0 | hand.foci.count  == 1 |
                                      hand.foci.count  == 2 | hand.foci.count  == 3 | hand.foci.count  == 4 )

length( (Curated_BivData  %>%  filter(  is.na(hand.foci.count) == T ) )$fileName )

table(cleanCurated_BivData$hand.foci.count, exclude = NULL)
#600 removed
```

@@

@@

Mouse.Table_BivData_4MM <- ddply(Curated_BivData, c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(  unique(fileName) ),
                      tot.biv = length(Obj.ID),

@@

#mouse level
mouse.total.skel <- ddply(.data=Total.SC_DF,
                          .(mouse),
                          summarize, 
                          ncells = length(unique(Original.Name)),
                          nmice = length(unique(mouse)),
                          mean.MLH1 = mean(nMLH1.foci, na.rm = TRUE),
                          var.MLH1 = var(nMLH1.foci),

                          mean.skel = mean(skel_size),
                          var.skel = var(skel_size),

                          mean.bin = mean(bin_size)
)

>>>>

@@

cleanCurated_BivData <- cleanCurated_BivData %>% filter(Obj.ID != "13sep18_28jun18_MOLF_m1_sp1_18.1_rev_14") #this object has wrongg position data

@@

Mouse.Table_BivData_4MM <- ddply(cleanCurated_BivData, c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(  unique(fileName) ),
                      tot.biv = length(Obj.ID),

@@

#mouse level
mouse.total.skel <- ddply(.data=Total.SC_DF,
                          .(mouse),
                          summarize, 
                          ncells = length(unique(Original.Name)),
                          nmice = length(unique(mouse)),
                          mean.MLH1 = mean(nMLH1.foci, na.rm = TRUE),
                          var.MLH1 = var(nMLH1.foci, na.rm = TRUE),

                          mean.skel = mean(skel_size, na.rm = TRUE),
                          var.skel = var(skel_size, na.rm = TRUE),

                          mean.bin = mean(bin_size, na.rm = TRUE)
)
